---
title: "Title_LDA"
author: "Jordan Sharples"
date: "`r Sys.Date()`"
output: 
  html_document:
    number_sections: yes
    toc: yes
editor_options: 
  chunk_output_type: inline
---

```{r, warning = FALSE, message = FALSE}
packages <- c("tidyverse", "skimr", "DataExplorer", "corrplot", "naniar","caret", "tidymodels","xgboost","randomForest")
install.packages(setdiff(packages, rownames(installed.packages())))


library(tidyverse)
library(skimr)
library(DataExplorer)
library(corrplot)
library(naniar)
library(DataExplorer)
library(ggplot2)
library(caret)
library(tidymodels)
library(xgboost)
library(randomForest)

library(tidyverse)
library(quanteda)
library(topicmodels)
library(tm)
library(tidytext)
library(quanteda.textstats)

df <- read.csv("Mastercontrol QAL Performance.csv")
```


```{r}
library(dplyr)
library(stringr)

df_clean <- df %>%
  mutate(across(where(is.character), ~ na_if(str_trim(.), "")))

library(naniar)

miss_var_summary(df_clean)

df_clean <- df_clean %>%
  mutate(
    acct.target.industry  = replace_na(acct.target.industry, "Unknown"),
    acct.territory.rollup = replace_na(acct.territory.rollup, "Unknown"),
    acct.tier.rollup      = replace_na(acct.tier.rollup, "Unknown"),
    contact.lead.title    = replace_na(contact.lead.title, "Unknown"),
    acct.manufacturing.model = replace_na(acct.manufacturing.model, "Unknown"),
    acct.primary.site.function = replace_na(acct.primary.site.function, "Unknown")
  )

library(forcats)

df_model <- df_clean %>%
  mutate(
    acct.target.industry  = fct_lump_min(as.factor(acct.target.industry), min = 50),
    acct.territory.rollup = fct_lump_min(as.factor(acct.territory.rollup), min = 50),
    acct.manufacturing.model = fct_lump_min(as.factor(acct.manufacturing.model), min = 50),
    acct.primary.site.function = fct_lump_min(as.factor(acct.primary.site.function), min = 50)
  )

df2 <- df_model %>%
  mutate(
    Target = if_else(
      next_stage__c %in% c("SQL","SQO","WON"),
      1,0
    )
  )

Mx_data <- df2 %>%
  filter(solution_rollup == "Mx")

# split data into test and train
set.seed(123)

train_index <- createDataPartition(Mx_data$Target, p = .7, list = FALSE)
train_data <- Mx_data[train_index,]
test_data <- Mx_data[-train_index,]
```

Feature engineering:

Because the "Contact/Lead Title" feature is considered extremely important in this application and because it is a free text field, we will perform
a latent dirichlet allocation to identify title categories. We will then explore how closely this category feature is tied to our target
variable.

```{r}
# Tokenize and preprocess the text data
tokens <- train_data$contact.lead.title %>%
    tokens(remove_punct = TRUE, remove_numbers = TRUE) %>%
    tokens_tolower() %>%
    tokens_remove(stopwords("en"))

cols <- textstat_collocations(tokens, min_count = 10)
tokens <- tokens_compound(tokens, pattern = cols)

tokens_test <- test_data$contact.lead.title %>%
    tokens(remove_punct = TRUE, remove_numbers = TRUE) %>%
    tokens_tolower() %>%
    tokens_remove(stopwords("en"))

cols_test <- textstat_collocations(tokens, min_count = 10)
tokens_test <- tokens_compound(tokens_test, pattern = cols)


# Convert tokens to DFM
dfm_train <- tokens %>%
  dfm()

dtm_train <- convert(dfm_train, to = "topicmodels")

dfm_test <- tokens_test %>%
  dfm()

dtm_test <- convert(dfm_test, to = "topicmodels")

# use perplexity to create elbow chart to determine ideal number of topics

k_values <- seq(2, 20, by = 1)
results <- sapply(k_values, function(k) {
  model <- LDA(dtm_train, k = k, method = "Gibbs", control = list(iter = 500))
  perplexity(model, newdata = dtm_test)
})

plot(k_values, results, type = "b", pch = 19, frame = FALSE,
     xlab = "Number of Topics", ylab = "Perplexity",
     main = "Perplexity Elbow Chart")

```

We will now model these topic using 12 as our k and add the topic membership as a feature to our dataframe

```{r, LDA Modeling}
# LDA
title_lda_train <- LDA(dtm_train, k = 12, control = list(seed = 123))

title_lda_test <- LDA(dtm_test, k = 12, control = list(seed = 123))

# see the top 5 words that constitute each category
terms(title_lda_train, 7)

# add category column to dataframe

# get category for each document
title_category_train <- topics(title_lda_train)
title_category_test <- topics(title_lda_test)

train_data$title.category <- as.factor(topics(title_lda_train))

test_data$title.category <- as.factor(topics(title_lda_test))
```

We can now see if there is any relationship between the categories identified in the previous step and our target variable
```{r}
train_data %>%
  group_by(title.category) %>%
  summarise(
    ConversionRate = mean(Target),
    Count = n(),
    .groups = "drop"
  ) %>%
  arrange(desc(ConversionRate)) %>%
  ggplot(aes(x = reorder(title.category, ConversionRate),
             y = ConversionRate,
             fill = ConversionRate)) +
  geom_col() +
  coord_flip() +
  labs(title = "Mx Conversion Rate by Identified Title Category",
       x = "Title Category",
       y = "Conversion Rate") +
  scale_fill_gradient(low = "lightblue", high = "steelblue") +
  theme_minimal() +
  
  geom_text(aes(label = Count), hjust = -0.2, color = "black", size = 4)

```
It looks like we have some very strong contenders for categories to target; specifically, category 6 and 7 are significantly higher than the average Mx conversion rate. It looks like the titles we are looking for are in operations management, quality management, manufacturing management, and senior engineers/scientists. Further analysis in the modeling phase will confirm this.

## Modeling using the new feature

We will start with a logisitic regression. This will output a probability of conversion for each of our leads. 
```{r LR_model_prep}
clean_train_data_modeling <- train_data %>%
 mutate(site_group = case_when(
  str_detect(acct.primary.site.function,"injectable|API|biologic|OSD") ~ "Pharma Manufacturing",
  str_detect(acct.primary.site.function,"device|IVD|surgical") ~ "Device Manufacturing",
  str_detect(acct.primary.site.function,"Non-manufacturing") ~ "Non-Manufacturing",
  TRUE ~ "Other Manufacturing"
 ))
clean_test_data_modeling <- test_data %>%
 mutate(site_group = case_when(
  str_detect(acct.primary.site.function,"injectable|API|biologic|OSD") ~ "Pharma Manufacturing",
  str_detect(acct.primary.site.function,"device|IVD|surgical") ~ "Device Manufacturing",
  str_detect(acct.primary.site.function,"Non-manufacturing") ~ "Non-Manufacturing",
  TRUE ~ "Other Manufacturing"
 ))
```

```{r LR_model}
LR_model <- glm(Target ~ acct.target.industry +
                  acct.territory.rollup +
                  acct.tier.rollup +
                  factor(title.category) + 
                  last.tactic.campaign.channel +
                  acct.manufacturing.model, # +
                  # Priority,
                data = clean_train_data_modeling,
                family = "binomial",
                weights = ifelse(clean_train_data_modeling$Target == 1,3,1))
summary(LR_model)
```
Let's look at the performance for this log model
```{r LR_Model_perfromance}

probs <- predict(LR_model, test_data, type = "response")

predicted <- ifelse(probs > .5,1,0)

confusionMatrix(as.factor(predicted), as.factor(test_data$Target))
```

```{r LR_AUC}
library(pROC)

roc_obj <- roc(as.numeric(test_data$Target), predicted)

auc_value <- auc(roc_obj)
print(auc_value)
```

```{r}
plot(roc_obj, col = "#1c61b6", lwd = 3, main = "ROC Curve for Logistic Regression Model with LDA categories and focus on MX")
abline(a = 0, b = 1, lty = 2, col = "gray")  # diagonal line for reference


auc_value <- auc(roc_obj)
legend("bottomright", legend = paste("AUC =", round(auc_value, 3)), col = "#1c61b6", lwd = 3)

```

## Random Forest Model
We run a Random Forest model using cross validation for hyperparameter testing
```{r random_forest}
cv_control <- trainControl(method = "cv", number = 5, sampling = "down", classProbs = TRUE)

clean_train_data_modeling$Target <- factor(clean_train_data_modeling$Target,
                            levels = c("0","1"),
                            labels = c("No","Yes"))

clean_test_data_modeling$Target <- factor(clean_test_data_modeling$Target,
                            levels = c("0","1"),
                            labels = c("No","Yes"))

tune_grid <- expand.grid(
  mtry = c(2,3,4),
  splitrule = c("gini", "extratrees"),
  min.node.size = c(1,5,10)
)
rf_model <- train(factor(Target) ~ acct.target.industry +
                    acct.tier.rollup +
                    acct.territory.rollup +
                    factor(title.category) +
                    last.tactic.campaign.channel +
                    Priority,
                  data = clean_train_data_modeling,
                  method = "ranger",
                  tuneGrid = tune_grid,
                  trControl = cv_control,
                  num.trees = 500,
                  importance = "impurity"
)
```

```{r random_forest_model}
print(rf_model)
```

```{r random_forest_performance}
rf_predictions <- predict(rf_model, test_data)

rf_probs <- predict(rf_model, newdata = clean_test_data_modeling, type = "prob")
yes_probs <- rf_probs$Yes

confusionMatrix(rf_predictions, factor(clean_test_data_modeling$Target))
```

```{r RF_ROC}
roc_rf <- roc(response = clean_test_data_modeling$Target, predictor = yes_probs)
auc_rf <- auc(roc_rf)
print(auc_rf)
```

```{r RF_AUC_Plot}
plot(roc_rf,
     col = "darkgreen",
     lwd = 3,
     main = "ROC Curve for Random Forest Model with LDA topics and only MX data")
abline(a = 0, b = 1, lty = 2, col = "gray")

legend("bottomright",
       legend = paste("AUC =", round(auc_rf,3)),
       col = "darkgreen",
       lwd = 3)
```

```{r rf_importance}
imp_scores <- varImp(rf_model)

print(imp_scores)

plot(imp_scores, top = 10, main = "Top 10 most important features")
```

```{r Gradient_boosted_tree_setup}
# set up cross validation
cv_control <- trainControl(
  method = "cv",
  number = 5,
  classProbs = TRUE,
  summaryFunction = twoClassSummary,
  sampling = "down"
)

# Parameter grid
xgb_grid <- expand.grid(
  nrounds = c(100,200,300),
  max_depth = c(3,6,9),
  eta = c(0.001, 0.01, 0.1),
  gamma = 0,
  colsample_bytree = c(1,0.8),
  min_child_weight = 1,
  subsample = 0.8
)

```

```{r, warning=FALSE, message=FALSE, XGB_training}
xgb_model <- suppressWarnings(train(
  factor(Target) ~ acct.target.industry +
                    acct.tier.rollup +
                    acct.territory.rollup +
                    factor(title.category) +
                    last.tactic.campaign.channel +
                    Priority, 
  data = clean_train_data_modeling, 
  method = "xgbTree",
  trControl = cv_control,
  tuneGrid = xgb_grid,
  verbosity = 0,
  metric = "ROC" 
))
```

```{r XGB_evaluation}
xgb_preds <- predict(xgb_model, newdata = clean_test_data_modeling)
confusionMatrix(xgb_preds, clean_test_data_modeling$Target)

xgb_probs <- predict(xgb_model, newdata = clean_test_data_modeling, type = "prob")
roc_obj <- roc(clean_test_data_modeling$Target, xgb_probs$Yes)

plot(roc_obj, col = "darkorange", lwd = 3, main = "XGBoost ROC Curve")
legend("bottomright",
       legend = paste("AUC = ", round(auc(roc_obj),3)),
       col = "darkorange",
       lwd = 3)
cat("TestAUC:", auc(roc_obj))
```

```{r XGB_Feature_importance}
xgb_imp <- varImp(xgb_model, scale = FALSE)

print(xgb_imp)
plot(xgb_imp, top=10)
```

```{r}
ICP_data <- clean_train_data_modeling %>%
  filter(
    acct.target.industry %in% c("Blood & Biologics", "Medical Device"),
    acct.tier.rollup %in% c("Small", "Medium"),
    acct.territory.rollup %in% c("Americas", "EMEA", "Japan")
  )
ICP_data$Target <- ifelse(ICP_data$Target == "Yes", 1, 0)
#reporting on conversion rates for ICP and Mx 
round(mean(ICP_data$Target), 2)
```